---
title: "FE621 HW4 Bonus Part"
author: "Shihao Zhang"
date: "2018-12-05"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Due to the large calculation of Monte Carlo Simulation inthe HW4, I have to seperate the HW4 orignal part and the bonus part to report in pdf. For the orignal problem part, please see FE621 HW4 Shihao Zhang Part1.

##(BONUS 1) SABR parameter estimation
```{r}
##question 1-----------------------------------------------------------------
#For this question, pick 2 yr matuarity
library('readxl')
setwd("C:\\Users\\fukaeri\\Desktop\\Stevens\\18FALL\\FE621\\HW")
mydataSABR<-read_excel("2017_2_15_mid.xlsx",col_names = TRUE)
#From equation(3) in paper,the at-the-money volatility sigma_ATM
Sigma_ATM<-function(alpha,beta,k,pho,v,t){
  term1<-((1-beta)^2)/24
  term2<-(alpha^2)/(k^(2-2*beta))
  term3<-(0.25*pho*beta*v*alpha)/(k^(1-beta))
  term4<-((2-3*pho^2)*(v^2))/24
  term5<-k^(1-beta)
  
  sig<-alpha*(1+(term1*term2+term3+term4)*t)/term5
  return(sig)
}
#Choose to use the 2rd yr data
Vol<-mydataSABR[seq(1,37,2),4]/100 #Volatility
K<-mydataSABR[seq(2,38,2),4]/100 #Strike Price

#Implement equation (5) in paper
f1<-function(x){
  sum=0
  for(i in 1:19){
    sum<-(Vol[i,1]-Sigma_ATM(x[1],0.5,K[i,1],x[2],x[3],2))^2+sum
  }                                   
  return(sum)
}
#Apply Optimization function
library("nloptr")
#beta=0.5&out put the result
Beta <- 0.5
parameter_0.5<-bobyqa(c(2,0.3,0.5),f1)
SABR.parameter_0.5 <- c(parameter_0.5$par[1],Beta,parameter_0.5$par[2],
                        parameter_0.5$par[3],parameter_0.5$value)
names(SABR.parameter_0.5) <- c('alpha','beta', 'rho', 'nu','SSE')
SABR.parameter_0.5 <- as.data.frame(SABR.parameter_0.5)
SABR.parameter_0.5
##question 2-----------------------------------------------------------------
#Set beta=0.7&0.4 repeat part1
#beta=0.7
f2<-function(x){
  sum=0
  for(i in 1:19){
    sum<-(Vol[i,1]-Sigma_ATM(x[1],0.7,K[i,1],x[2],x[3],2))^2+sum
  }                                   
  return(sum)
}
Beta <- 0.7
parameter_0.7<-bobyqa(c(2,0.3,0.5),f2)
SABR.parameter_0.7 <- c(parameter_0.7$par[1],Beta,parameter_0.7$par[2],
                        parameter_0.7$par[3],parameter_0.7$value)
names(SABR.parameter_0.7) <- c('alpha','beta', 'rho', 'nu','SSE')
SABR.parameter_0.7 <- as.data.frame(SABR.parameter_0.7)
SABR.parameter_0.7
#beta=0.4
f3<-function(x){
  sum=0
  for(i in 1:19){
    sum<-(Vol[i,1]-Sigma_ATM(x[1],0.4,K[i,1],x[2],x[3],2))^2+sum
  }                                   
  return(sum)
}
Beta <- 0.4
parameter_0.4<-bobyqa(c(2,0.3,0.5),f3)
SABR.parameter_0.4 <- c(parameter_0.4$par[1],Beta,parameter_0.4$par[2],
                        parameter_0.4$par[3],parameter_0.4$value)
names(SABR.parameter_0.4) <- c('alpha','beta', 'rho', 'nu','SSE')
SABR.parameter_0.4 <- as.data.frame(SABR.parameter_0.4)
SABR.parameter_0.4
##question 3-----------------------------------------------------------------
mycomparetable <- cbind(SABR.parameter_0.4,SABR.parameter_0.5,SABR.parameter_0.7)
mycomparetable
#Comments:By comparsion, we notice that alpha increase when beta increase.
#Rho is decreasing when beta increasing(however it only change slightly)
#And nu is on opposition from the rho's direction
##question 4-----------------------------------------------------------------
mycomparetable
#Comments:Still by the comparsion table, the model gives us the best estimation
#when beta is 0.4. At this time, we obtain alpha=.2556546, rho=-0.7589516,
#nu=2.8442623, and the smallest SEE=0.0888966


##question 5-----------------------------------------------------------------
alpha_best <- SABR.parameter_0.4[1,]
beta_best <- SABR.parameter_0.4[2,]
rho_best <- SABR.parameter_0.4[3,]
nu_best <- SABR.parameter_0.4[4,]
#Choose to use the 3rd yr data
K2 <- mydataSABR[seq(2,38,2), 3]/100
Vol2 <- mydataSABR[seq(1,38,2), 3]/100
vol_ATM <- matrix(NA,19,1)


for(i in 1:19){
  vol_ATM[i,1] <- Sigma_ATM(alpha_best,beta_best,K2[i,],rho_best,nu_best,2)
}
vol_atm <- matrix(NA,19,1)
for(i in 1:19){
  vol_atm[i,1] <- Sigma_ATM(alpha_best,beta_best,K2[i,],rho_best,nu_best,1)
}
compare2 <- as.matrix(cbind(Vol2 - vol_ATM,Vol2 - vol_atm))
colnames(compare2) <- c('1-year','2-year')
print(compare2)

plot(x=as.matrix(K2),y=vol_atm,col="blue",type="p",
     main="1-year Swaption Volatility with 2 year parameters",
     xlab="strike", ylab="Volatility", ylim = c(0, 2)) 
points(x=as.matrix(K2),y=as.matrix(Vol2),col="red") 
#Comments:Estimate Volatility is blue points.
#And the real Volatility is red points.
#They converge when strike price is high.
```
##(BONUS 2) Sim.DiffProc question
Comments: #1.When we apply Euler method to estimate the stochastic differential equations, the Euler scheme produces the discretization when delta t is approaching zero, and we have the increments (X[t+deltat]-X[t]) with certain mean(drift) and variance(diffusion). Then we can estimate the parameter by change the question into optimazing the log-likelihood, and we can select the optimization method by the argument(optim.method). #2.When we apply the Ozaki method, the diffusion term(sigma) is supposed to be constant. And we can transform general SDE with a constant diffusion coefficient using the Lamperti transform.
```{r}
set.seed(1)
#Given the information
S0 <- 100
theta1 <- 1000
theta2 <- -10
theta3 <- 0.8
theta4 <- 0.5
dt <- 1/365
Tm <- 4
#Simulate the path
library(Sim.DiffProc)
f <- expression((theta1+theta2*x))
g <- expression(theta3*x^theta4)
sim <- snssde1d(drift=f,diffusion=g,x0=S0,M=1,N=1460,Dt=dt)
mydata <- sim$X
#Estimation of model
fx <- expression(theta[1]+theta[2]*x) ##drift coefficient 
gx <- expression(theta[3]*x^theta[4]) ##diffusion coefficient
#1.Euler method
fitmod_Euler <- fitsde(data=mydata,drift=fx,diffusion=gx,start=list(theta1=999,
                 theta2=10,theta3=1,theta4=1),pmle="euler")
coef_Euler <- coef(fitmod_Euler)
true <- true_value <- c(theta1,theta2,theta3,theta4) ##True parameters
bias_Euler <- true-coef(fitmod_Euler)
AIC_Euler <- AIC(fitmod_Euler)
#2.Ozaki method
fitmod_Ozaki <- fitsde(data=mydata,drift=fx,diffusion=gx,start=list(theta1=999,
                 theta2=10,theta3=1,theta4=1),pmle="ozaki")
coef_Ozaki <- coef(fitmod_Ozaki)
bias_Ozaki <- true-coef(fitmod_Ozaki)
AIC_Ozaki  <- AIC(fitmod_Ozaki)
#3.Shoji-Ozaki method
fitmod_Shoji <- fitsde(data=mydata,drift=fx,diffusion=gx,start=list(theta1=999,
                 theta2=10,theta3=1,theta4=1),pmle="shoji")
coef_Shoji <- coef(fitmod_Shoji)
bias_Shoji <- true-coef(fitmod_Shoji)
AIC_Shoji  <- AIC(fitmod_Shoji)
#4.Kessler method
fitmod_Kessler <- fitsde(data=mydata,drift=fx,diffusion=gx,start=list(theta1=999,
                 theta2=10,theta3=1,theta4=1),pmle="kessler")
coef_Kessler <- coef(fitmod_Kessler)
bias_Kessler <- true-coef(fitmod_Kessler)
AIC_Kessler  <- AIC(fitmod_Kessler)
#Create Table and Report
#true value and estimated coef
myresult1 <- cbind(true_value,coef_Euler,coef_Ozaki,coef_Shoji,coef_Kessler)
myresult1
#Bias
myresult2 <- cbind(bias_Euler,bias_Ozaki,bias_Shoji,bias_Kessler)
myresult2
#AIC
#AIC deals with the trade-off between the goodness of fit
#of the model,AIC lower is preferred.
myresult3 <- cbind(AIC_Euler,AIC_Ozaki,AIC_Shoji,AIC_Kessler)
myresult3
#Comments:The Euler,Ozaki,Shoji-Ozaki scheme all fit the process at pretty much same level,
#with almost identical parameter estimation, Bias and AIC.
#However, when it turn to Kessler scheme, the Kessler scheme might be the best for fitting
#the process with the lowest AIC(AIC=8), but the paramater bias for theta2 is high
#(and negative).
```

