---
title: "FE621 HW2"
author: "Shihao Zhang"
date: "2018-09-30"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Problem 1: Binomial/Trinomial Tree Basics
```{r}
#1.Using additive binomiall tree
#Calculate the values of the European Call and put option
#The difference between call and put option is the strike price,
#I use a factor cp which represent 1 or -1, in that way
#to calculate both options.
Binomial_tree <- function(isCall, isAmerican, K, Tm, S0, sig, r=0.0192,
                          N=200)
  {
  #Precompute constants
  dt <-  Tm/N
  v <-  r-0.5*sig^2
  u <-  sqrt(sig^2*dt+(v*dt)^2) #dxu
  d <- -u
  p <- 0.5+0.5*(v*dt/u) #probability
  disc <- exp(-r*dt) #discount factor
  M <- N+1
  cp <- ifelse(isCall, 1, -1) #factor cp with 1 or -1
  
  #Intialize asset prices
  V = S = matrix(0, nrow = M, ncol = M, dimnames = list(
    paste("State", 1:(N+1), sep = ""), paste("T=",0:N, sep = "")))
  S[1,1] <- S0
  for (j in 2:M) {
    S[1,j] <- S[1,j-1]*exp(u)
    for (i in 2:j) {
      S[i,j] <- S[i-1,j-1]*exp(d)
    }
  }
  
  #Intialize option values at maturity
  for (j in 1:M) {
    V[M-j+1,M] <- max(0, cp*(S[M-j+1,M]-K))
  }
  
  #Step backwards through the tree
  for (j in (M-1):1) {
    for (i in 1:j) {
      V[i,j] <- disc*(p*V[i,j+1]+(1-p)*V[i+1,j+1])
      if(isAmerican){
        V[i,j] <- max(V[i,j],cp*(S[i,j]-K))
      }
    }
  }
  #Return the price
  return(V[1,1])
}
Binomial_tree(isCall = T,isAmerican = F, K=100, Tm=1, S0=100, sig=0.2,
              r=0.06,N=3)
#Here I use the same parameter in figure 2.11 in textbook to check the model
#And I obtain the same result as 11.5920
```
2.Download Option prices
I choose AMZN's options. And the expiry date is 2018-10-19,2018-11-02,2018-10-26,separately.
```{r}
library(TTR)
library(quantmod)
Aequity=function(symbol){
  A_equity <- getSymbols(symbol,src="yahoo",from="2018-09-28",to="2018-10-03",auto.assign = FALSE)
}
AMZN_price <- Aequity("AMZN")
A_price <- AMZN_price$AMZN.Adjusted[3]
AM1=getOptionChain("AMZN",Exp = '2018-10-19',src = "yahoo",auto.assign = FALSE)#Expiry 2018-10-19 #Expire in 17 days
AM2=getOptionChain("AMZN",Exp = '2018-11-02',src = "yahoo",auto.assign = FALSE)#Expiry 2018-11-02 #Expire in 31 days
AM3=getOptionChain("AMZN",Exp = '2018-10-26',src = "yahoo",auto.assign = FALSE)#Expiry 2018-10-26 #Expire in 24 days

# Black-Scholes Option Value
BSmodel <- function(S0, Sigma, t, K, r, optionType){
  d1 = (log(S0/K) + (r + (Sigma^2)/2) * t)/(Sigma * sqrt(t))
  d2 = d1 - Sigma * sqrt(t)
  if(optionType == 'call'){ 
    call = S0 * pnorm(d1) - K * exp(-r * t) * pnorm(d2) 
    return(call)
  }else if(optionType == "put"){
    put = K * exp(-r * t) * pnorm(-d2) - S0 * pnorm(-d1)
    return(put)
  }
}
#Implement the Bisection method
vrange=c(0,1)
t1=0
bisection=function(f, vrange, tol){
  while((vrange[2]-vrange[1]) >= tol){
    x=0.5*(vrange[1]+vrange[2])
if(f(x)*f(vrange[2])>0)
  {
  vrange[2]=x
}else if(f(x)*f(vrange[2])<0){
  vrange[1]=x
}
  t1=1+t1
}
return(x)
}

# Using bisection and BS model
# Calculate the implied volatility for AM_option1
r <- 0.0216 #the risk free rate
AMcall1=AM1$calls$Strike[1:20]
AMimpcall1=AMimpcall2=AMimpcall3=AMimput1=AMimput2=AMimput3=c()
# Call
for(i in 1:length(AMcall1)){
  AMvolc1 = function(sigma){
    BSmodel(A_price, sigma, 17/252,AMcall1[i], r, "call") - 0.5 * (AM1$calls$Bid[i] +AM1$calls$Ask[i])
  }
  AMimpcall1[i] = bisection(AMvolc1, vrange, 1e-2)
}
#Put
AMput1=AM1$puts$Strike[1:20]
for(i in 1:length(AMput1)){
  AMvolp1 = function(sigma){
    BSmodel(A_price, sigma, 17/252,AMput1[i], r, "put") - 0.5 * (AM1$puts$Bid[i] + AM1$puts$Ask[i])
  }
  AMimput1[i] = bisection(AMvolp1, vrange, 1e-2)
}

# Second Option
AMcall2=AM2$calls$Strike[1:20]

# Call
for(i in 1:length(AMcall2)){
  AMvolc2 = function(sigma){
    BSmodel(A_price, sigma, 31/252,AMcall2[i], r, "call") - 0.5 * (AM2$calls$Bid[i] + AM2$calls$Ask[i])
  }
  AMimpcall2[i] = bisection(AMvolc2, vrange, 1e-6)
}

#Put
AMput2=AM2$puts$Strike[1:20]
for(i in 1:length(AMput2)){
  AMvolp2 = function(sigma){
    BSmodel(A_price, sigma, 31/252,AMput2[i], r, "put") - 0.5 * (AM2$puts$Bid[i] + AM2$puts$Ask[i])
  }
  AMimput2[i] = bisection(AMvolp2, vrange, 1e-6)
}

# Third Option

AMcall3=AM3$calls$Strike[1:20]

# Call
for(i in 1:length(AMcall3)){
  AMvolc3 = function(sigma){
    BSmodel(A_price, sigma, 24/252,AMcall3[i], r, "call") - 0.5 * (AM3$calls$Bid[i] + AM3$calls$Ask[i])
  }
  AMimpcall3[i] = bisection(AMvolc3, vrange, 1e-6)
}

#Put
AMput3=AM3$puts$Strike[1:20]
for(i in 1:length(AMput3)){
  AMvolp3 = function(sigma){
    BSmodel(A_price, sigma, 24/252,AMput3[i], r, "put") - 0.5 * (AM3$puts$Bid[i] + AM3$puts$Ask[i])
  }
  AMimput3[i] = bisection(AMvolp3, vrange, 1e-6)
}


# Using BS Model and Binomial tree calculating option price
TTM1=17/252
TTM2=31/252
TTM3=24/252

# By BS model
r <- 0.0216 #the risk free rate
Acall1=Acall2=Acall3=Aput1=Aput2=Aput3=c()
# First AMZN Option
for (i in 1:length(AMcall1)){
  Acall1[i] = BSmodel(A_price, AMimpcall1[i], TTM1, AMcall1[i], r, "call")
}

for (i in 1:length(AMput1)){
  Aput1[i] = BSmodel(A_price, AMimput1[i], TTM1, AMput1[i], r, "put")
}
#Second AMZN Option
for (i in 1:length(AMcall2)){
  Acall2[i] = BSmodel(A_price, AMimpcall2[i], TTM2, AMcall2[i], r, "call")
}

for (i in 1:length(AMput2)){
  Aput2[i] = BSmodel(A_price, AMimput2[i], TTM2, AMput2[i], r, "put")
}
#Third Amzn Option
for (i in 1:length(AMcall3)){
  Acall3[i] = BSmodel(A_price, AMimpcall3[i], TTM3, AMcall3[i], r, "call")
}

for (i in 1:length(AMput3)){
  Aput3[i] = BSmodel(A_price, AMimput3[i], TTM3, AMput3[i], r, "put")
}

#By Binomial Tree
r <- 0.0216 #the risk free rate
N <- 200
BiAcall1=BiAcall2=BiAcall3=BiAput1=BiAput2=BiAput3=c() #Names Options by Binomial
# first option
for (i in 1:length(AMcall1)){
  BiAcall1[i] = Binomial_tree(isCall=T, isAmerican=F, AMcall1[i], TTM1, A_price, AMimpcall1[i], r,N)
}
for (i in 1:length(AMput1)){
  BiAput1[i] = Binomial_tree(isCall=F, isAmerican=F, AMput1[i], TTM1, A_price, AMimput1[i], r,N)
}
#Second option
for (i in 1:length(AMcall2)){
  BiAcall2[i] = Binomial_tree(isCall=T, isAmerican=F, AMcall2[i], TTM2, A_price, AMimpcall2[i], r,N)
}
for (i in 1:length(AMput2)){
  BiAput2[i] = Binomial_tree(isCall=F, isAmerican=F, AMput2[i], TTM2, A_price, AMimput2[i], r,N)
}
#Third option
for (i in 1:length(AMcall3)){
  BiAcall3[i] = Binomial_tree(isCall=T, isAmerican=F, AMcall3[i], TTM3, A_price, AMimpcall3[i], r,N)
}
for (i in 1:length(AMput3)){
  BiAput3[i] = Binomial_tree(isCall=F, isAmerican=F, AMput3[i], TTM3, A_price, AMimput3[i], r,N)
}
#Combine in a table
# Create a table to compare call and put by two methods
table_call <- data.frame(Acall1, BiAcall1,Acall2,BiAcall2,Acall3,BiAcall3)
table_put <- data.frame(Aput1,BiAput1,Aput2,BiAput2,Aput3,BiAput3)
table_call
table_put#A is calculated by BSmodel, BiA is calculated by Binomiall Tree
```
3.plot the absolute error
```{r}
N <-  seq(50,400,by=50) #steps
error1 = c() #Calculate error
for (i in 1:length(N)) {
  error1[i] = abs(BSmodel(A_price, AMimpcall1[i], TTM1, AMcall1[i], r, "call")
                 -Binomial_tree(isCall=T, isAmerican=F, AMcall1[i], TTM1, A_price, AMimpcall1[i], r,N[i]))
}
error2 = c() #Calculate error
for (i in 1:length(N)) {
  error2[i] = abs(BSmodel(A_price, AMimpcall2[i], TTM2, AMcall2[i], r, "call")
                 -Binomial_tree(isCall=T, isAmerican=F, AMcall2[i], TTM2, A_price, AMimpcall2[i], r,N[i]))
}
error3 = c() #Calculate error
for (i in 1:length(N)) {
  error3[i] = abs(BSmodel(A_price, AMimpcall3[i], TTM3, AMcall3[i], r, "call")
                 -Binomial_tree(isCall=T, isAmerican=F, AMcall3[i], TTM3, A_price, AMimpcall3[i], r,N[i]))
}
plot(N, error1, type="l", xlab = "N",ylab = "error")
plot(N, error2, type="l", xlab = "N",ylab = "error")
plot(N, error3, type="l", xlab = "N",ylab = "error")
#We can see that as the steps going up, the error will decrease. 
#However, we still have some fluctuate in the middle steps.
```
4.Calculate the American option
```{r}
#Implement an additive binomial tree
N <- 200
r <- 0.0216 #the risk free rate
BiAcall1_Am=BiAcall2_Am=BiAcall3_Am=BiAput1_Am=BiAput2_Am=BiAput3_Am=c()
# first option
for (i in 1:length(AMcall1)){
  BiAcall1_Am[i] = Binomial_tree(isCall=T, isAmerican=T, AMcall1[i], TTM1, A_price, AMimpcall1[i], r,N)
}
for (i in 1:length(AMput1)){
  BiAput1_Am[i] = Binomial_tree(isCall=F, isAmerican=T, AMput1[i], TTM1, A_price, AMimput1[i], r,N)
}
#Second option
for (i in 1:length(AMcall2)){
  BiAcall2_Am[i] = Binomial_tree(isCall=T, isAmerican=T, AMcall2[i], TTM2, A_price, AMimpcall2[i], r,N)
}
for (i in 1:length(AMput2)){
  BiAput2_Am[i] = Binomial_tree(isCall=F, isAmerican=T, AMput2[i], TTM2, A_price, AMimput2[i], r,N)
}
#Third option
for (i in 1:length(AMcall3)){
  BiAcall3_Am[i] = Binomial_tree(isCall=T, isAmerican=T, AMcall3[i], TTM3, A_price, AMimpcall3[i], r,N)
}
for (i in 1:length(AMput3)){
  BiAput3_Am[i] = Binomial_tree(isCall=F, isAmerican=T, AMput3[i], TTM3, A_price, AMimput3[i], r,N)
}
table_call_Am <- data.frame(BiAcall1_Am,BiAcall2_Am,BiAcall3_Am)
table_put_Am <- data.frame(BiAput1_Am,BiAput2_Am,BiAput3_Am)
head(table_call_Am)
head(table_put_Am)
```

5.Create a table which contains Bid and Ask
values, Black Scholes price, European and American prices
```{r}
# Create Call table
table_call1 <- data.frame(AM1$calls$Bid[1:20], AM1$calls$Ask[1:20], Acall1, BiAcall1, BiAcall1_Am)
table_call2 <- data.frame(AM2$calls$Bid[1:20], AM2$calls$Ask[1:20], Acall2, BiAcall2, BiAcall2_Am)
table_call3 <- data.frame(AM3$calls$Bid[1:20], AM3$calls$Ask[1:20], Acall3, BiAcall3, BiAcall3_Am)
colnames(table_call1)=colnames(table_call2)=colnames(table_call3)=
  c("Call Bid", "Call Ask", "Call BS price", "European Call", "American Call")
table_call_all <- rbind(table_call1,table_call2,table_call3)
# Create Put table
table_put1 = data.frame(AM1$puts$Bid[1:20], AM1$puts$Ask[1:20], Aput1, BiAput1, BiAput1_Am)
table_put2 = data.frame(AM2$puts$Bid[1:20], AM2$puts$Ask[1:20], Aput2, BiAput2, BiAput2_Am)
table_put3 = data.frame(AM3$puts$Bid[1:20], AM3$puts$Ask[1:20], Aput3, BiAput3, BiAput3_Am)
colnames(table_put1)=colnames(table_put2)=colnames(table_put3)=
  c("Put Bid", "Put Ask", "Put BS price", "European Put", "American Put")
table_put_all <- rbind(table_put1,table_put2,table_put3)
#Merge in one table
table_all <- cbind(table_call_all,table_put_all)
#From the data, the price between BSmodel and Binomial Tree is really close.
#And the price is all between Bid and Ask.
#The price is more accurate when time to maturity is closing.
#And because all the 3 option I choose will expiry less than 31days.
#The call price between European and American option is same, while some difference in put price. 
```

6.Compare implied volatility
```{r}
#Implement Bisenction&Binomial Tree to find implied volatility for American Options
impcall1=impcall2=impcall3=imput1=imput2=imput3=c()
N <- 50
#First Option
#Call volatility
for(i in 1:length(AMcall1)){
  volc1 <- function(sigma){
    Binomial_tree(isCall=T, isAmerican=T, AMcall1[i], TTM1, A_price, sigma, r,N)
    - 0.5 * (AM1$calls$Bid[i] + AM1$calls$Ask[i])
  }
  impcall1[i] = bisection(volc1, vrange, 1e-6)}
#Put volatility
for(i in 1:length(AMput1)){
  volp1 = function(sigma){
    Binomial_tree(isCall=F, isAmerican=T, AMput1[i], TTM1, A_price, sigma, r,N)
    - 0.5 * (AM1$puts$Bid[i] + AM1$puts$Ask[i])
  }
  imput1[i] = bisection(volp1, vrange, 1e-6)}
# Second Option
for(i in 1:length(AMcall2)){
  volc2 <- function(sigma){
    Binomial_tree(isCall=T, isAmerican=T, AMcall2[i], TTM2, A_price, sigma, r,N)
    - 0.5 * (AM2$calls$Bid[i] + AM2$calls$Ask[i])
  }
  impcall2[i] = bisection(volc2, vrange, 1e-6)}
for(i in 1:length(AMput2)){
  volp2 = function(sigma){
    Binomial_tree(isCall=F, isAmerican=T, AMput2[i], TTM2, A_price, sigma, r,N)
    - 0.5 * (AM2$puts$Bid[i] + AM2$puts$Ask[i])
  }
  imput2[i] = bisection(volp2, vrange, 1e-6)}
# Third Option
for(i in 1:length(AMcall3)){
  volc3 <- function(sigma){
    Binomial_tree(isCall=T, isAmerican=T, AMcall3[i], TTM3, A_price, sigma, r,N)
    - 0.5 * (AM3$calls$Bid[i] + AM3$calls$Ask[i])
  }
  impcall3[i] = bisection(volc3, vrange, 1e-6)}
#Put volatility
for(i in 1:length(AMput3)){
  volp3 = function(sigma){
    Binomial_tree(isCall=F, isAmerican=T, AMput3[i], TTM3, A_price, sigma, r,N)
    - 0.5 * (AM3$puts$Bid[i] + AM3$puts$Ask[i])
  }
  imput3[i] = bisection(volp3, vrange, 1e-6)}

#compare implied Vol by BS model and Binomial Tree model

#Call Implied Vol
table_call_BSBI <- data.frame(AMimpcall1,impcall1,AMimpcall2,impcall2,AMimpcall3,impcall3)
colnames(table_call_BSBI) <- c("BS Call1", "BiTree Call1", "BS Call2","BiTree Call2","BS Call3","BiTree Call3")
table_put_BSBI = data.frame(AMimput1,imput1,AMimput2,imput2,AMimput3,imput3)
colnames(table_put_BSBI) = c("BS Put1", "BiTree Put1","BS Put2", "BiTree Put2","BS Put3", "BiTree Put3")
table_call_BSBI#Call vol
table_put_BSBI#Put vol
#From Observation, for call volatility by the 2 models are very close.
#However, for put volatility, the Binomial Tree model provide more smaller volatility.
#I guess the reason is that the Binomial Tree is less sensitive to volatility.
```
7.Implement a trinomial tree to price an American Put option
```{r}
#Implement a trinomial tree
Trinomial_tree <- function(isCall,isAmerican,S0,K,Tm,sig,r,div,N){
  #Precompute constants
  dt <- Tm/N
  dx <- sig*sqrt(3*dt)
  nu <- r - div - 0.5*sig^2
  edx <- exp(dx)
  pu <- 0.5*((sig^2*dt+nu^2*dt^2)/(dx^2)+nu*dt/dx)
  pd <- 0.5*((sig^2*dt+nu^2*dt^2)/(dx^2)-nu*dt/dx)
  pm <- 1 - pu - pd
  disc <- exp(-r*dt)
  #Call-Put Flag
  cp <- ifelse(isCall, 1, -1)
  #initialize asset prices 
  S_mat <- matrix(ncol=2*N+1,nrow=N+1)
  S_mat[1,N+1]<-S0
  for (i in 1:N) {
    S_mat[i+1,(N+1-i):(N+1+i)]<- S0*(exp(((-i:i)*dx)))
  }
  #initialize option values
  V_mat <- matrix(ncol=2*N+1,nrow=N+1)
  V_mat[N+1,] <- pmax(cp*(S_mat[N+1,]-K),0)
  #step back through the tree
  for(i in N:1){
    V_mat[i,(N-i+2):(i+N)]<-disc*(pu*V_mat[i+1,(N-i+3):(i+N+1)]
                                  +pm*V_mat[i+1,(N-i+2):(i+N)]
                                  +pd*V_mat[i+1,(N-i+1):(i+N-1)])
    if(isAmerican){
      V_mat[i,(N-i+2):(i+N)] <- max(V_mat[i,(N-i+2):(i+N)],
                                    cp*(S_mat[i,(N-i+2):(i+N)]-K))
    }
    }
  return(Price=V_mat[1,N+1])
}
#Price an American Put option
#Given the data
N <- 3
r <- 0.0216 #the risk free rate
div <- 0
TriAput1_Am <- c()
for (i in 1:length(AMput1)){
  TriAput1_Am[i] = Trinomial_tree(isCall=F, isAmerican=F, A_price, AMput1[i], TTM1, AMimput1[i], r,div,N)
}
mytable <- cbind(TriAput1_Am,BiAput1_Am)
mytable#Compare with Binomial model
```







Problem 2.Adapting the Binomial tree to time varying coefficients
```{r}
#1
f1 <- function(x){
  0.05*(1+0.01*x)
}
f2 <- function(x){
  0.3*(1+0.005*x)
}
#Set coefficients
i <- seq(0,11,1)
r <- sapply(i,f1)
sig <- sapply(i,f2)
v <- r-sig^2/2
dx <- 0.05 #choose dx

#Calculate delat_t,delta_p,and probabilities
dt <- (-sig^2+sqrt(sig^4+4*v^2*dx^2))/(2*v^2)
p <- 1/2+v*dt/(2*dx)
mytable <- cbind(i,r,sig,v,dt,p)
mytable
#2.
f3 <- function(x){
    sum((-sig[1:2]^2+sqrt(sig[1:2]^4+4*v[1:2]^2*x^2))/(2*v[1:2]^2))-0.5
}
dx <- bisection(f3,vrange, 1e-6)#Apply the bisection method
dx#determine the optimal value of dx
#3.
Binomial_tree(isCall=T, isAmerican=F, 10, 0.5, 10, mean(sig), mean(r),
                          N=11)
Binomial_tree(isCall=F, isAmerican=F, 10, 0.5, 10, mean(sig), mean(r),
                          N=11)
#So the call option price is 1.0112 and put option price is 0.7518
```
Problem 3.Dealing with discrete cash dividends
For this problem I used the model provided on book "Implementing Derivative Models".
```{r}
#Price call and put option
#Given the data provided
r <- 0.001
sig <- 0.4
S0 <- 100
K <- 90
Tm <- 4/24
div <- 0.6
Tau <- 1/24

#Since the delta_t is constants, and T=4/24, Tau=1/24,
#Obviously we should construct a tree with steps N=4.
#And the dividends is paid at node(1,0);(1,1)
Tau_Step <- 1 #The step that the dividends is paid
Binomial_tree1 <- function(isCall, isAmerican, K, Tm, S0, sig, r,
                          N=4)
  {
  #Precompute constants
  dt <-  Tm/N
  v <-  r-0.5*sig^2
  u <-  sqrt(sig^2*dt+(v*dt)^2) #dxu
  d <- -u
  p <- 0.5+0.5*(v*dt/u) #probability
  disc <- exp(-r*dt) #discount factor
  dpu <- disc*p
  dpd <- disc*(1-p)
  edxud <- exp(2*u)
  edxd <- exp(-1*u)
  M <- N+1
  cp <- ifelse(isCall, 1, -1) #factor cp with 1 or -1
  
  #Intialize asset prices
  V = S = matrix(0, nrow = M, ncol = M, dimnames = list(
    paste("State", 1:(N+1), sep = ""), paste("T=",0:N, sep = "")))
  S[M,M] <- (S0-div*exp(-r*Tau))*exp(N*d)
  for (i in M:2) {
    S[i-1,M] <- S[i,M]*edxud
  }
  for (j in M:2) {
    S[1,j-1] <- S[1,j]/exp(u)
    for (i in M:2) {
      S[i-1,j-1] <- S[i,j]/exp(d)
    }
  }
  S[Tau_Step,Tau_Step] <- S[Tau_Step,Tau_Step+1]/exp(u)+div*exp(-r*(Tau-Tau)) #Add dividend on stock
  
  
  #Intialize option values at maturity
  for (j in 1:M) {
    V[M-j+1,M] <- max(0, cp*(S[M-j+1,M]-K))
  }
  
  #Step backwards through the tree
  for (j in (M-1):1) {
    for (i in 1:j) {
      V[i,j] <- disc*(p*V[i,j+1]+(1-p)*V[i+1,j+1])
      if(isAmerican){
        V[i,j] <- max(V[i,j],cp*(S[i,j]-K))
      }
    }
  }
  #Return the price
  return(V[1,1])
}
Call_Option_Price <- Binomial_tree1(isCall=T, isAmerican=T, K, Tm, S0, sig, r,N=4)
Put_Option_Price <- Binomial_tree1(isCall=F, isAmerican=T, K, Tm, S0, sig, r,N=4)
Results <- cbind(Call_Option_Price,Put_Option_Price)
Results #The Price of derivatives
```




























