---
title: "Untitled"
author: "Shihao Zhang"
date: "2018-10-26"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
HW3
Problem 1
1.Implement the Explicit Finite Difference method
```{r}
Explicit_finite <- function(isCall,K,Tm,S0,sigma,r,div,N,Nj){
  #precompute constants
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  nu <- r-div-0.5*sigma^2
  edx <- exp(dx)
  pu <- 0.5*dt*((sigma/dx)^2+nu/dx)
  pm <- 1-dt*(sigma/dx)^2-r*dt
  pd <- 0.5*dt*((sigma/dx)^2-nu/dx)
  #initialize asset prices at maturity
  V=S=matrix(0,nrow=2*Nj+1,ncol=N+1)
  cp <- ifelse(isCall,1,-1)
  S[2*Nj+1,N+1] <- S0*exp(-Nj*dx)
  for (i in (2*Nj):1) {
    S[i,N+1]=S[i+1,N+1]*exp(dx)
  }
  #initial option value at maturity
  for (i in (2*Nj+1):1) {
    V[i,N+1] <- max(0,cp*(S[i,N+1]-K))
  }
  #step back through lattice
  for (j in N:1) {
    for (i in (2*Nj):2) {
      V[i,j] <- pu*V[i-1,j+1]+pm*V[i,j+1]+pd*V[i+1,j+1]
    }
    #boundary conditions
    stockTerm <- ifelse(isCall,S[1,N+1]-S[2,N+1],
                        S[2*Nj,N+1]-S[2*Nj+1,N+1])
    V[2*Nj+1,j] <- V[2*Nj,j]+ifelse(isCall,0,stockTerm)
    V[1,j] <- V[2,j]+ifelse(isCall,stockTerm,0)
  }
  V[Nj+1,1]
}
```


2.Implement the Implicit Finite Difference method
```{r}
Implicit_finite <- function(isCall,K,Tm,S0,sigma,r,div,N,Nj){
  #Implicit Finite Difference Method with i times,2*i+1 final nodes
  #precompute constants
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  nu <- r-div-0.5*sigma^2
  edx <- exp(dx)
  pu <- -0.5*dt*((sigma/dx)^2+nu/dx)
  pm <-  1.0+dt* (sigma/dx)^2+r*dt
  pd <- -0.5*dt*((sigma/dx)^2-nu/dx)
  
  firstRow <- 1
  nRows = lastRow = 2*Nj+1
  firstCol <- 1
  middleRow <- Nj+1
  nCols = lastCol = N+1
  
  cp <- ifelse(isCall,1,-1)
  
  #initialize asset prices, derivative prices
  pmp=pp=V=S=matrix(0,nrow=nRows,ncol=nCols)
  S[lastRow,lastCol] <- S0*exp(-Nj*dx)
  for (j in (lastRow-1):firstRow) {
    S[j,lastCol]=S[j+1,lastCol]*exp(dx)
  }
  
  #initial option value at maturity
  for (j in (firstRow):lastRow) {
    V[j,lastCol] <- max(0,cp*(S[j,lastCol]-K))
  }

  #compute derivative boundary condition
  lambdaL <- ifelse(isCall,0,(S[lastRow,lastCol]-S[lastRow-1,lastCol]))
  lambdaU <- ifelse(isCall,(S[firstRow,lastCol]-S[firstRow+1,lastCol]),0)  
  
  #step back through lattice
  for (i in (lastCol-1):firstCol) {
    #solve implicit tridiagonal system
    #substitute boundary condition at j=-Nj into j=-Nj+1
    pmp[(lastRow-1),i] <- pm+pd
    pp[(lastRow-1),i]  <- V[(lastRow-1),lastCol]+pd*lambdaL
    #eliminate upper diagonal
    for (j in (lastRow-2):(firstRow+1)) {
        pmp[j,i] <- pm-pu*pd/pmp[j+1,i]
        pp[j,i] <- V[j,i+1]-pp[j+1,i]*pd/pmp[j+1,i]
    }
    #use boundary condition at j=Nj and equation at j=Nj-1
    V[firstRow,i] <- (pp[(firstRow+1),i]+pmp[(firstRow+1),i]
                                  *lambdaU/(pu+pmp[(firstRow+1),i]))
    V[(firstRow-1),i] <- V[(firstRow),i]-lambdaU
    #back-substitution
    for (j in (firstRow+2):lastRow) {
        V[j,i] <- (pp[j,i]-pu*V[j-1,i])/pmp[j,i]
    }
    V[lastRow,i] <- V[(lastRow-1),i]-lambdaL
  }
  V[Nj+1,1]
}

Implicit_finite(T,100,1,100,0.2,0.06,0.03,3,3)
```

3.Implement the Crank-Nicolson Finite Difference method
```{r}
Crank_Nicolson_finite <- function(isCall,K,Tm,S0,sigma,r,div,N,Nj){
  #precompute constants
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  nu <- r-div-0.5*sigma^2
  edx <- exp(dx)
  pu <- -0.25    *dt*((sigma/dx)^2+nu/dx)
  pm <-  1.0 +0.5*dt* (sigma/dx)^2+ 0.5*r*dt
  pd <- -0.25    *dt*((sigma/dx)^2-nu/dx)
  
  firstRow <- 1
  nRows = lastRow = 2*Nj+1
  firstCol <- 1
  middleRow <- Nj+1
  nCols = lastCol = N+1
  
  cp <- ifelse(isCall,1,-1)
  
  #initialize asset prices, derivative prices
  pmp=pp=V=S=matrix(0,nrow=nRows,ncol=nCols)
  S[lastRow,lastCol] <- S0*exp(-Nj*dx)
  for (j in (lastRow-1):firstRow) {
    S[j,lastCol]=S[j+1,lastCol]*exp(dx)
  }
  
  #initial option value at maturity
  for (j in (firstRow):lastRow) {
    V[j,lastCol] <- max(0,cp*(S[j,lastCol]-K))
  }

  #compute derivative boundary condition
  lambdaL <- ifelse(isCall,0,(S[lastRow,lastCol]-S[lastRow-1,lastCol]))
  lambdaU <- ifelse(isCall,(S[firstRow,lastCol]-S[firstRow+1,lastCol]),0)
  
  #step back through lattice
  for (i in (lastCol-1):firstCol) {
    #solve system
    #substitute boundary condition at j=-Nj into j=-Nj+1
    pmp[(lastRow-1),i] <- pm+pd
    pp[(lastRow-1),i]  <- -pu*V[(lastRow-2),lastCol]-(pm-2)*V[(lastRow-1),lastCol]-pd*V[(lastRow),lastCol]+pd*lambdaL
    #eliminate upper diagonal
    for (j in (lastRow-2):(firstRow+1)) {
        pmp[j,i] <- pm-pu*pd/pmp[j+1,i]
        pp[j,i] <- -pu*V[j-1,i+1]-(pm-2)*V[j,i+1]-pd*V[j+1,i+1]-pp[j+1,i]*pd/pmp[j+1,i]
    }
    #use boundary condition at j=Nj and equation at j=Nj-1
    V[firstRow,i] <- (pp[(firstRow+1),i]+pmp[(firstRow+1),i]
                                  *lambdaU/(pu+pmp[(firstRow+1),i]))
    V[(firstRow-1),i] <- V[(firstRow),i]-lambdaU
    #back-substitution
    for (j in (firstRow+2):lastRow) {
        V[j,i] <- (pp[j,i]-pu*V[j-1,i])/pmp[j,i]
    }
    V[lastRow,i] <- V[(lastRow-1),i]-lambdaL
  }
  V[Nj+1,1]
}
N <- 1221
Nj <- 60
Crank_Nicolson_finite(T,100,1,100,0.25,0.06,0.03,N,Nj)
Crank_Nicolson_finite(F,100,1,100,0.25,0.06,0.03,N,Nj)
```
4.Calculate and report the price for European Call and Put using all the FD
methods
```{r}
#Given the data
K <- 100
Tm <- 1
S0 <- 100
sigma <- 0.25
r <- 0.06
div <- 0.03
#Assuming N&Nj
N <- 1000
Nj <- 60

c1 <- Explicit_finite(T,K,Tm,S0,sigma,r,div,N,Nj)
p1 <- Explicit_finite(F,K,Tm,S0,sigma,r,div,N,Nj)
c2 <- Implicit_finite(T,K,Tm,S0,sigma,r,div,N,Nj)
p2 <- Implicit_finite(F,K,Tm,S0,sigma,r,div,N,Nj)
c3 <- Crank_Nicolson_finite(T,K,Tm,S0,sigma,r,div,N,Nj)
p3 <- Crank_Nicolson_finite(F,K,Tm,S0,sigma,r,div,N,Nj)
call <- c(c1,c2,c3)
put <- c(p1,p2,p3)
tablecp <- data.frame(call,put)
rownames(tablecp) <- c("Explicit_finite","Implicit_finite","Crank_Nicolson_finite")
tablecp
```
5.plot on the same graph the implicit finite updating coefficients A;B;C
```{r}
#Given the data
K <- 100
Tm <- 1
S0 <- 100
r <- 0.06
div <- 0.03
#Calculate
sigma <- seq(0.05,0.60,by=0.05)
dt <- Tm/N
dx <- sigma*sqrt(3*dt)
nu <- r-div-0.5*sigma^2
pu <- -0.5*dt*((sigma/dx)^2+nu/dx)#A
pm <-  1.0+dt* (sigma/dx)^2+r*dt#B
pd <- -0.5*dt*((sigma/dx)^2-nu/dx)#C
par(mfrow=c(1,3))
plot(pu~sigma)
plot(pm~sigma)
plot(pd~sigma)
#By observation, we can see as sigma goes up, pu goes up, pm remain constant
#for a certain level, pd goes down clearly. pu is concave and pd is convex.
#Also pu&pd is negative.
```
6.Estimate the number
```{r}
for (i in 1:10000) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- dx^2+Tm/N
  if(error < 0.001){
    break
  }
}
N
Nj
```
7.We have to substrate result in EFD,IFD,CNFD method, and use black-scholes price to calculate the N and Nj.
```{r}
#BSmodel
BSmodel <- function(s,t,t2,K,sigma,r,type){
d1 <- (log(s/K)+(r+0.5*sigma^2)*(t2-t))/sigma*sqrt(t2-t)
2
d2 <- d1-sigma*sqrt(t2-t)
if(type == "calls")
c <- s*pnorm(d1)-K*(exp(-r*(t2-t)))*pnorm(d2)
if(type == "puts")
c <- K*(exp(-r*(t2-t)))*pnorm(-d2)-s*pnorm(-d1)
return(c)
}
BSC <- BSmodel(100,0,1,100,0.25,0.03,"calls")
BSP <- BSmodel(100,0,1,100,0.25,0.03,"puts")
#Given the data
K <- 100
Tm <- 1
S0 <- 100
sigma <- 0.25
r <- 0.06
div <- 0.03
#call error for explicit finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Explicit_finite(T,K,Tm,S0,sigma,r,div,N,Nj)-BSC)
  if(error < 0.001){
    break
  }
}
result1 <- paste("Explicit call:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)
#put error for explicit finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Explicit_finite(F,K,Tm,S0,sigma,r,div,N,Nj)-BSP)
  if(error < 0.001){
    break
  }
}
result2 <- paste("Explicit put:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)
#call error for implicit finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Implicit_finite(T,K,Tm,S0,sigma,r,div,N,Nj)-BSC)
  if(error < 0.001){
    break
  }
}
result3 <- paste("Implicit call:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)
#put error for implicit finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Implicit_finite(F,K,Tm,S0,sigma,r,div,N,Nj)-BSP)
  if(error < 0.001){
    break
  }
}
result4 <- paste("Implicit put:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)

#call error for Crank Nicolson finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Implicit_finite(T,K,Tm,S0,sigma,r,div,N,Nj)-BSC)
  if(error < 0.001){
    break
  }
}
result5 <- paste("Crank Nicolson call:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)
#put error for Crank Nicolson finite
for (i in 1:100) {
  sigma <- 0.25
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- abs(Implicit_finite(F,K,Tm,S0,sigma,r,div,N,Nj)-BSP)
  if(error < 0.001){
    break
  }
}
result6 <- paste("Crank Nicolson put:","N=",N,",Nj=",Nj,",dx=",dx,",dt=",dt)
result1
result2
result3
result4
result5
result6#Due to the environment of my computer, I can only iterate up to 100times

```
8.Calculate the hedge sensitivities for the European call option
```{r}
#Given the data
K <- 100
Tm <- 1
S0 <- 100
sigma <- 0.25
r <- 0.06
div <- 0.03
N <- 1221
Nj <- 60
isCall <- T
delta <- 0.01
#Calculate with sensitivity =0.01
Delta <- ((Explicit_finite(isCall,K,Tm,S0+delta,sigma,r,div,N,Nj))-
  (Explicit_finite(isCall,K,Tm,S0-delta,sigma,r,div,N,Nj)))/(2*delta)
Gamma <- ((Explicit_finite(isCall,K,Tm,S0+delta,sigma,r,div,N,Nj))
          -2*(Explicit_finite(isCall,K,Tm,S0,sigma,r,div,N,Nj))
          +(Explicit_finite(isCall,K,Tm,S0-delta,sigma,r,div,N,Nj)))/(delta*delta)
Theta <- ((Explicit_finite(isCall,K,Tm+delta,S0,sigma,r,div,N,Nj))-
  (Explicit_finite(isCall,K,Tm-delta,S0,sigma,r,div,N,Nj)))/(2*delta)
Vega <- ((Explicit_finite(isCall,K,Tm,S0,sigma+delta,r,div,N,Nj))-
  (Explicit_finite(isCall,K,Tm,S0,sigma-delta,r,div,N,Nj)))/(2*delta)
#The greeks
thegreeks <- data.frame(Delta,Gamma,Theta,Vega)
thegreeks


```


Problem 2. Finite difference method applied to market data
a.Download Option prices&calculate impilied volatility
I choose the AAPL's options, and the expiry date is 2018-11-16,2018-12-21,2019-01-18, seperately
```{r}
#set the current short-term interest rate
r <- 0.022#federal rate at 2018-10-28
library(TTR)
library(quantmod)
Aequity=function(symbol){
A_equity <- getSymbols(symbol,src="yahoo",from="2018-10-26",to="2018-10-27",auto.assign = FALSE)
}
AAPL <- Aequity("AAPL")
AAPL <- AAPL$AAPL.Adjusted[1]#AAPL stock price
A_price <- AAPL
A1 <- getOptionChain("AAPL",Exp = '2018-11-16',src = "yahoo",auto.assign = FALSE)#Option1
A2 <- getOptionChain("AAPL",Exp = '2018-12-21',src = "yahoo",auto.assign = FALSE)#Option2
A3 <- getOptionChain("AAPL",Exp = '2019-01-18',src = "yahoo",auto.assign = FALSE)#Option3
TTM1 <- 19/365
TTM2 <- 54/365
TTM3 <- 82/365
# Black-Scholes Option Value
BSmodel <- function(S0, Sigma, t, K, r, optionType){
  d1 = (log(S0/K) + (r + (Sigma^2)/2) * t)/(Sigma * sqrt(t))
  d2 = d1 - Sigma * sqrt(t)
  if(optionType == 'call'){ 
    call = S0 * pnorm(d1) - K * exp(-r * t) * pnorm(d2) 
    return(call)
  }else if(optionType == "put"){
    put = K * exp(-r * t) * pnorm(-d2) - S0 * pnorm(-d1)
    return(put)
  }
}

#Implement the Bisection method
vrange=c(0,1)
t1=0
bisection=function(f, vrange, tol){
  while((vrange[2]-vrange[1]) >= tol){
    x=0.5*(vrange[1]+vrange[2])
if(f(x)*f(vrange[2])>0)
  {
  vrange[2]=x
}else if(f(x)*f(vrange[2])<0){
  vrange[1]=x
}
  t1=1+t1
}
return(x)
}
AM1 <- A1
AM2 <- A2
AM3 <- A3
# Using bisection and BS model
# Calculate the implied volatility for AM_option1
AMcall1=AM1$calls$Strike[1:10]
AMimpcall1=AMimpcall2=AMimpcall3=AMimput1=AMimput2=AMimput3=c()
# Call
for(i in 1:length(AMcall1)){
  AMvolc1 = function(sigma){
    BSmodel(A_price, sigma, TTM1,AMcall1[i], r, "call") - 0.5 * (AM1$calls$Bid[i] +AM1$calls$Ask[i])
  }
  AMimpcall1[i] = bisection(AMvolc1, vrange, 1e-2)
}
#Put
AMput1=AM1$puts$Strike[1:10]
for(i in 1:length(AMput1)){
  AMvolp1 = function(sigma){
    BSmodel(A_price, sigma, TTM1,AMput1[i], r, "put") - 0.5 * (AM1$puts$Bid[i] + AM1$puts$Ask[i])
  }
  AMimput1[i] = bisection(AMvolp1, vrange, 1e-2)
}

# Second Option
AMcall2=AM2$calls$Strike[1:10]

# Call
for(i in 1:length(AMcall2)){
  AMvolc2 = function(sigma){
    BSmodel(A_price, sigma, TTM2,AMcall2[i], r, "call") - 0.5 * (AM2$calls$Bid[i] + AM2$calls$Ask[i])
  }
  AMimpcall2[i] = bisection(AMvolc2, vrange, 1e-6)
}

#Put
AMput2=AM2$puts$Strike[1:10]
for(i in 1:length(AMput2)){
  AMvolp2 = function(sigma){
    BSmodel(A_price, sigma, TTM2,AMput2[i], r, "put") - 0.5 * (AM2$puts$Bid[i] + AM2$puts$Ask[i])
  }
  AMimput2[i] = bisection(AMvolp2, vrange, 1e-6)
}

# Third Option

AMcall3=AM3$calls$Strike[1:10]

# Call
for(i in 1:length(AMcall3)){
  AMvolc3 = function(sigma){
    BSmodel(A_price, sigma, TTM3,AMcall3[i], r, "call") - 0.5 * (AM3$calls$Bid[i] + AM3$calls$Ask[i])
  }
  AMimpcall3[i] = bisection(AMvolc3, vrange, 1e-6)
}

#Put
AMput3=AM3$puts$Strike[1:10]
for(i in 1:length(AMput3)){
  AMvolp3 = function(sigma){
    BSmodel(A_price, sigma, TTM3,AMput3[i], r, "put") - 0.5 * (AM3$puts$Bid[i] + AM3$puts$Ask[i])
  }
  AMimput3[i] = bisection(AMvolp3, vrange, 1e-6)
}
result <- data.frame(AMimpcall1,AMimput1,AMimpcall2,AMimput2,AMimpcall3,AMimput3)
result
```
b.Use the Explicit, Implicit, and Crank-Nicolson Finite Difference schemes
```{r}
#Use the calculated implied volatility to obtain a space parameter deltax
#Call 1
sigmax <- AMimpcall1
space_parameter <- function(sigmax){
  for (i in 1:10000) {
  sigma <- sigmax
  Tm <- 1
  Nj <- i
  #the stability&convergence condition
  N <- ceiling(3*((2*Nj+1)/6)^2)
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  error <- dx^2+Tm/N
  if(error < 0.001){
    break
  }
  }
  return(c(N,Nj))
}
parameter <- sapply(sigmax, space_parameter)
N_Call1 <- parameter[1,]
Nj_Call1 <- parameter[2,]

#Similiarly do for put1,call2,put2,call3,put3
#Put1
sigmax <- AMimput1
parameter <- sapply(sigmax, space_parameter)
N_Put1 <- parameter[1,]
Nj_Put1 <- parameter[2,]
#call2
sigmax <- AMimpcall2
parameter <- sapply(sigmax, space_parameter)
N_Call2 <- parameter[1,]
Nj_Call2 <- parameter[2,]
#Put2
sigmax <- AMimput2
parameter <- sapply(sigmax, space_parameter)
N_Put2 <- parameter[1,]
Nj_Put2 <- parameter[2,]
#Call3
sigmax <- AMimpcall3
parameter <- sapply(sigmax, space_parameter)
N_Call3 <- parameter[1,]
Nj_Call3 <- parameter[2,]
#Put3
sigmax <- AMimput3
parameter <- sapply(sigmax, space_parameter)
N_Put3 <- parameter[1,]
Nj_Put3 <- parameter[2,]





#Use explicit finite difference schemes
#Call1
list_Call <- cbind(isCall,K,Tm,S0,sigma,r,div,N,Nj)
EFD_Call1 <- c()
for (i in 1:10) {
isCall[i] <- T
K[i] <- AM1$calls$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimpcall1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Call1[i]
Nj[i] <- Nj_Call1[i]
EFD_Call1[i] <- Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}

#Put1
EFD_Put1 <- c()
for (i in 1:10) {
isCall[i] <- F
K[i] <- AM1$puts$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimput1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Put1[i]
Nj[i] <- Nj_Put1[i]
EFD_Put1[i] <- Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}

#Use implicit finite difference schemes
#Call1
list_Call <- cbind(isCall,K,Tm,S0,sigma,r,div,N,Nj)
IFD_Call1 <- c()
for (i in 1:10) {
isCall[i] <- T
K[i] <- AM1$calls$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimpcall1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Call1[i]
Nj[i] <- Nj_Call1[i]
IFD_Call1[i] <- Implicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}

#Put1
IFD_Put1 <- c()
for (i in 1:10) {
isCall[i] <- F
K[i] <- AM1$puts$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimput1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Put1[i]
Nj[i] <- Nj_Put1[i]
IFD_Put1[i] <- Implicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}


#Use Crank-Nicolson finite difference schemes
#Call1
list_Call <- cbind(isCall,K,Tm,S0,sigma,r,div,N,Nj)
CNFD_Call1 <- c()
for (i in 1:10) {
isCall[i] <- T
K[i] <- AM1$calls$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimpcall1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Call1[i]
Nj[i] <- Nj_Call1[i]
CNFD_Call1[i] <- Crank_Nicolson_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}

#Put1
CNFD_Put1 <- c()
for (i in 1:10) {
isCall[i] <- F
K[i] <- AM1$puts$Strike[i]
Tm[i] <- TTM1
S0[i] <- as.numeric(A_price)
sigma[i] <- AMimput1[i]
r[i] <- 0.022
div[i] <- 0
N[i] <- N_Put1[i]
Nj[i] <- Nj_Put1[i]
CNFD_Put1[i] <- Crank_Nicolson_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])
}

table_result <- cbind(EFD_Call1,EFD_Put1,IFD_Call1,IFD_Put1,CNFD_Call1,CNFD_Put1)
table_result#This is result I use EFD,IFD,CNFD calculating option price for 1 month maturity for AAPL
```
c.Calculating corresponding Greeks using EFD
```{r}
#For Call
#Calculate with sensitivity =0.01
delta1 <- matrix(rep(0.01,10),nrow=10,ncol=1)
TTM1_10 <- matrix(rep(TTM1,10),nrow=10,ncol=1)
S0_10 <- matrix(rep(as.numeric(A_price),10),nrow=10,ncol=1)
r_10 <- matrix(rep(0.022,10),nrow=10,ncol=1)
div_10 <- matrix(rep(0,10),nrow=10,ncol=1)
isCall_10 <- matrix(rep(T,10),nrow=10,ncol=1)
#Delta
delta <- matrix(nrow=10,ncol=1)
isCall <- matrix(nrow=10,ncol=1)
K <- matrix(nrow=10,ncol=1)
Tm <- matrix(nrow=10,ncol=1)
S0 <- matrix(nrow=10,ncol=1)
sigma <- matrix(nrow=10,ncol=1)
r <- matrix(nrow=10,ncol=1)
div <- matrix(nrow=10,ncol=1)
N <- matrix(nrow=10,ncol=1)
Nj <- matrix(nrow=10,ncol=1)
EFD_Call1_Dealta <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
delta[i] <- delta1[i]
isCall[i] <- isCall_10[i]
K[i] <- AM1$calls$Strike[i]
Tm[i] <- TTM1_10[i]
S0[i] <- S0_10[i]
sigma[i] <- AMimpcall1[i]
r[i] <- r_10[i]
div[i] <- div_10[i]
N[i] <- N_Call1[i]
Nj[i] <- Nj_Call1[i]
}
for (i in 1:10) {
  EFD_Call1_Dealta[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i]+delta[i],sigma[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i],S0[i]-delta[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}
#Gamma
EFD_Call1_Gamma <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Call1_Gamma[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i]+delta[i],sigma[i],r[i],div[i],N[i],Nj[i]))
          -2*(Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i]))
          +(Explicit_finite(isCall[i],K[i],Tm[i],S0[i]-delta[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(delta[i]*delta[i])
}
#Theta
EFD_Call1_Theta <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Call1_Theta[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i]+delta[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i]-delta[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}
#Vega
EFD_Call1_Vega <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Call1_Vega[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i]+delta[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i]-delta[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}

##----------
#For put
#Calculate with sensitivity =0.01
delta1 <- matrix(rep(0.01,10),nrow=10,ncol=1)
TTM1_10 <- matrix(rep(TTM1,10),nrow=10,ncol=1)
S0_10 <- matrix(rep(as.numeric(A_price),10),nrow=10,ncol=1)
r_10 <- matrix(rep(0.022,10),nrow=10,ncol=1)
div_10 <- matrix(rep(0,10),nrow=10,ncol=1)
isCall_10 <- matrix(rep(F,10),nrow=10,ncol=1)
#Delta
delta <- matrix(nrow=10,ncol=1)
isCall <- matrix(nrow=10,ncol=1)
K <- matrix(nrow=10,ncol=1)
Tm <- matrix(nrow=10,ncol=1)
S0 <- matrix(nrow=10,ncol=1)
sigma <- matrix(nrow=10,ncol=1)
r <- matrix(nrow=10,ncol=1)
div <- matrix(nrow=10,ncol=1)
N <- matrix(nrow=10,ncol=1)
Nj <- matrix(nrow=10,ncol=1)

for (i in 1:10) {
delta[i] <- delta1[i]
isCall[i] <- isCall_10[i]
K[i] <- AM1$puts$Strike[i]
Tm[i] <- TTM1_10[i]
S0[i] <- S0_10[i]
sigma[i] <- AMimput1[i]
r[i] <- r_10[i]
div[i] <- div_10[i]
N[i] <- N_Put1[i]
Nj[i] <- Nj_Put1[i]
}
#Delta
EFD_Put1_Dealta <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Put1_Dealta[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i]+delta[i],sigma[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i],S0[i]-delta[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}
#Gamma
EFD_Put1_Gamma <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Put1_Gamma[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i]+delta[i],sigma[i],r[i],div[i],N[i],Nj[i]))
          -2*(Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i]))
          +(Explicit_finite(isCall[i],K[i],Tm[i],S0[i]-delta[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(delta[i]*delta[i])
}
#Theta
EFD_Put1_Theta <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Put1_Theta[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i]+delta[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i]-delta[i],S0[i],sigma[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}
#Vega
EFD_Put1_Vega <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  EFD_Put1_Vega[i] <- ((Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i]+delta[i],r[i],div[i],N[i],Nj[i]))-
  (Explicit_finite(isCall[i],K[i],Tm[i],S0[i],sigma[i]-delta[i],r[i],div[i],N[i],Nj[i])))/(2*delta[i])
}


#The greeks
EFDthegreeks <- data.frame(EFD_Call1_Dealta,EFD_Put1_Dealta,EFD_Call1_Gamma,EFD_Put1_Gamma,
                           EFD_Call1_Theta,EFD_Put1_Theta,EFD_Call1_Vega,EFD_Put1_Vega)
EFDthegreeks
```
d.Create a table
```{r}
#For call
#Time to maturity T
TTM1_10 <- matrix(rep(TTM1,10),nrow=10,ncol=1)
Tm_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  Tm_Call1[i] <- TTM1_10[i]
}
#Strike price
K_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  K_Call1[i] <- AM1$calls$Strike[i]
}
#Type of the option
Type_Call1 <- matrix("Call",nrow=10,ncol=1)
#Ask price A
A_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  A_Call1[i] <- AM1$calls$Ask[i]
}
#Bid price B
B_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  B_Call1[i] <- AM1$calls$Bid[i]
}
#Market price Cm
Cm_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  Cm_Call1[i] <- (A_Call1[i]+B_Call1[i])/2
}
#Implied volatility 
sigma_BSMimp_Call1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  sigma_BSMimp_Call1[i] <- AMimpcall1[i]
}
#option price calculated with EFD, IFD, and CNFD
#EFD_Call1,EFD_Put1,IFD_Call1,IFD_Put1,CNFD_Call1,CNFD_Put1

#For put
#Time to maturity T
TTM1_10 <- matrix(rep(TTM1,10),nrow=10,ncol=1)
Tm_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  Tm_Put1[i] <- TTM1_10[i]
}
#Strike price
K_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  K_Put1[i] <- AM1$puts$Strike[i]
}
#Type of the option
Type_Put1 <- matrix("Put",nrow=10,ncol=1)
#Ask price A
A_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  A_Put1[i] <- AM1$puts$Ask[i]
}
#Bid price B
B_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  B_Put1[i] <- AM1$puts$Bid[i]
}
#Market price Cm
Cm_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  Cm_Put1[i] <- (A_Put1[i]+B_Put1[i])/2
}
#Implied volatility 
sigma_BSMimp_Put1 <- matrix(nrow=10,ncol=1)
for (i in 1:10) {
  sigma_BSMimp_Put1[i] <- AMimput1[i]
}

Result_table_Call1 <- cbind(Tm_Call1,K_Call1,Type_Call1,A_Call1,B_Call1,Cm_Call1,sigma_BSMimp_Call1,EFD_Call1,IFD_Call1,CNFD_Call1)
colnames(Result_table_Call1) <- c("Time to maturity T","Strike price","Type of the option","Ask price A","Bid price B","Market price Cm",
                                  "Implied volatility ","EFD_Call1","IFD_Call1","CNFD_Call1 ")

Result_table_Put1 <- cbind(Tm_Put1,K_Put1,Type_Put1,A_Put1,B_Put1,Cm_Put1,sigma_BSMimp_Put1,EFD_Put1,IFD_Put1,CNFD_Put1)
colnames(Result_table_Put1) <- c("Time to maturity T","Strike price","Type of the option","Ask price A","Bid price B","Market price Cm",
                                  "Implied volatility ","EFD_Put1","IFD_Put1","CNFD_Put1 ")
Result_table_Call1
Result_table_Put1

#Figure for Call
par(mfrow=c(1,2)) 
plot(A_Call1,col="red",ylab = "Call1 Ask,Bid,Market Price&Option price")
par(new = TRUE)
plot(B_Call1,col="green",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(Cm_Call1,col="blue",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(EFD_Call1,col="cyan",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(IFD_Call1,col="gray",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(CNFD_Call1,col="yellow",axes = FALSE,xlab = "", ylab = "")
#----
#Figure for put
plot(A_Put1,col="red",ylab = "Put1 Ask,Bid,Market Price&Option price")
par(new = TRUE)
plot(B_Put1,col="green",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(Cm_Put1,col="blue",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(EFD_Put1,col="cyan",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(IFD_Put1,col="gray",axes = FALSE,xlab = "", ylab = "")
par(new = TRUE)
plot(CNFD_Put1,col="yellow",axes = FALSE,xlab = "", ylab = "")
#We can observe that the stock price is actually fallen between bid&ask spread
#And for AAPL stock, call option is close to stock price and put option is fall below stock price
```




























Problem 3.
1.Discretize the derivatives
Please see attached files with hand-written equation


2.What do you observe about the process of updating coefficients?
For the updating coefficients, We can observe that the value of S cannot be too large. Otherwise pm could be negative,large number. Consider the three equation pu,pm&pd, we notice that it is similiar to the tirnomial tree model with Black-scholes equation. Also we can approximate sum(p)=1-r*delat t as exp(-r*delat t), with discount factor.


3.Implement the scheme
```{r}
#Parameter
isCall <- F #Put option
S0 <- 100
K <- 100
Tm <- 1
sigma <- sqrt(0.4*S0^1.5)
N <- 2000
Nj <- 80

EFD_scheme <- function(isCall,K,Tm,S0,sigma,N,Nj){
  #precompute constants
  dt <- Tm/N
  dx <- sigma*sqrt(3*dt)
  edx <- exp(dx)
  pu <- dt*(0.2*S0^1.5/dx^2+sin(S0)/dx)
  pm <- 1-dt*(0.4*S0^1.5/dx^2)-r*dt
  pd <- dt*(0.2*S0^1.5/dx^2-sin(S0)/dx)
  #initialize asset prices at maturity
  V=S=matrix(0,nrow=2*Nj+1,ncol=N+1)
  cp <- ifelse(isCall,1,-1)
  S[2*Nj+1,N+1] <- S0*exp(-Nj*dx)
  for (i in (2*Nj):1) {
    S[i,N+1]=S[i+1,N+1]*exp(dx)
  }
  #initial option value at maturity
  for (i in (2*Nj+1):1) {
    V[i,N+1] <- max(0,cp*(S[i,N+1]-K))
  }
  #step back through lattice
  for (j in N:1) {
    for (i in (2*Nj):2) {
      V[i,j] <- pu*V[i-1,j+1]+pm*V[i,j+1]+pd*V[i+1,j+1]
    }
    #boundary conditions
    stockTerm <- ifelse(isCall,S[1,N+1]-S[2,N+1],
                        S[2*Nj,N+1]-S[2*Nj+1,N+1])
    V[2*Nj+1,j] <- V[2*Nj,j]+ifelse(isCall,0,stockTerm)
    V[1,j] <- V[2,j]+ifelse(isCall,stockTerm,0)
  }
  V[Nj+1,1]
}
EFD_scheme(F,100,1,100,20,2000,80)
```













































